Title of the publication

### 2016-07-12 documentation/EnTrI2/manuscript.tex
Computed ancestral insertion indices for nodes on species trees, Ran upsetr on hieranoid outputs, Added SL3261 to the sequences and started rerunning codes, Made a poster for SMBE

\keywords{Keyword1 | Keyword2 | Keyword3} % When adding keywords, separate each term with a straight line: |

@@

% \abbreviations{}
\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}

@@

\section{Results}
\textcolor{red}{\{An explanation of the experiment\}}

\textbf{Clustering orthologous and paralogous genes.} To study the essentiality of genes in 12 strains depicted in Fig~\ref{fig:tree}, We needed to cluster sets of orthologous genes in these strain. Plenty of methods are proposed for this purpose. Altenhoff et al.\@ have compared 15 of these methods \cite{altenhoff_standardized_2016} and shown that Hieranoid \cite{schreiber_hieranoid:_2013} is among three methods that keep a balance between precision and recall. We have used Hieranoid to cluster the sets of orthologous genes. In addition, we intended to study the essentiality of genes in paralogous genes. For this, we have developed a program that clusters all homologous genes using Jackhmmer from HMMER3 package \cite{mistry_challenges_2013}.

@@

\begin{materials}

\end{materials}

@@

%----------------------------------------------------------------------------------------
%	FIGURES AND TABLES
%----------------------------------------------------------------------------------------
\begin{figure}
\includegraphics[scale=0.25]{consensustree.pdf}
\label{fig:tree}
\caption{Species tree. How is it made?}
\end{figure}

>>>>

\keywords{essentiality | conservation | transposon insertion} % When adding keywords, separate each term with a straight line: |

@@

% \abbreviations{}
%\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}

@@

\section{Bias}

\section{Gene classes}
\subsection{Genus specific}
\subsection{Single copy}
\subsection{Multi-copy}
\section{Evolution of essentiality}

\section{Case study of genes}
\subsection{Core genes}
\subsection{Accessory genes}

@@

\begin{materials}
\textbf{Clustering orthologous and paralogous genes.} To study the essentiality of genes in 12 our strains, We needed to cluster sets of orthologous genes in these strain. Plenty of methods are proposed for this purpose. Altenhoff et al.\@ have compared 15 of these methods \cite{altenhoff_standardized_2016} and shown that Hieranoid \cite{schreiber_hieranoid:_2013} is among three methods that keep a balance between precision and recall. We have used Hieranoid to cluster the sets of orthologous genes. In addition, we intended to study the essentiality of genes in paralogous genes. For this, we have developed a program that clusters all homologous genes using Jackhmmer from HMMER3 package \cite{mistry_challenges_2013}.
\end{materials}

@@

%----------------------------------------------------------------------------------------
%	FIGURES AND TABLES
%----------------------------------------------------------------------------------------
